Reassessing the role of theory and machine learning in forecasting civil conflict

### 2020-09-18 paper.Rmd
moar pie
mdw

Throwing a bunch of variables that you think are related to a dependent variable and popping then Into a non parametric model is not a theory-driven model.

>>>>

There is another type of theory we can define ostensibly. It consists of taking a variety of variables that putatively relate to another (dependent) variable and running a non-parametric model such as a logistic regression with this set of variables.  This even weaker form of theory is the most widespread use of theory in the contemporary social sciences, and it is the type of theory that is employed in B\&S:
